Verifying Concurrent Search Structure Templates for C Programs using VST

### 2023-04-22 concurrency/CONCUR 2023/paper.tex
answer William's question

>>>>

\than{The most challenging aspect of the project was the proofs involving traversal. It took me a considerable amount of time to understand the pre- and post-conditions, as well as determining the appropriate loop invariants. I found myself frequently switching between proving the \texttt{insertOp} and \texttt{traverse} functions in order to combine all elements. However, once I had completed the \texttt{traverse} proofs, everything became much easier.}
